### 2019-09-12 2-Chapters/6-Chapter/nonstatbandits/NonStatB.tex
Removed raw inclusion of https://hal.inria.fr/hal-02006471

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.09\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_1.pdf}
    \caption{Problem $1$: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on only one arm at a time (\ie, $C=4$).
        The means are in $[0,1]$, and there are $C+1=5$ stationary intervals of equal lengths.
        Some changes do not modify the optimal arm (\eg, at $T=1000$ and $T=4000$) and others do.
    }
    \label{fig:6:Problem_1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.09\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_2.pdf}
    \caption{Problem $2$: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on all arms (\ie, $C=12$).
        The means are again in $[0,1]$, and there are also $C+1=5$ stationary intervals of equal lengths.
        % Some changes do not modify the optimal arm, but the mean of each arm does change at all change-points.
    }
    \label{fig:6:Problem_2}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_5.pdf}
    \caption{Problem $3$: $K=6$, $T=20000$, $C=19$ changes occur on most arms at $\Upsilon=8$ break-points.}
    \label{fig:6:Problem_5}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_4.pdf}
    \caption{Problem $4$: $K=3$, $T=5000$, $C=12$ changes occur on all arms at $\Upsilon=4$ break-points.}
    % \caption{\textbf{Problem 4}: $K=3$ arms with $T=5000$, $\Upsilon=4$ changes occur on all arms at a time (\ie, $C=12$).}
    \label{fig:6:Problem_4}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/6_Problems/Problem_6.pdf}
    \caption{Pb $5$: $K=5$, $T=100000$, $C=179$ changes occur on some arms at $\Upsilon=81$ break-points.}
    % \caption{\textbf{Problem 5}: $K=5$, $T=100000$, $\Upsilon=81$ changes occurring on some arms at every time ($C=179$).}
    \label{fig:6:Problem_6}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.15\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/SP__K3_T5000_N1000__9_algos_pb1/main____env1-1_1316297932259102962.pdf}
    \caption{Mean regret as a function of time, $R_t$ for horizon $T = 5000$, for problem 1.}
    \label{fig:6:meanRegretPb1}
\end{figure}

% -----------------------------------------------------------------
\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.09\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/SP__K3_T5000_N1000__9_algos_pb2/main____env1-1_7882655236216606305.pdf}
    \caption{Mean regret as a function of time, $R_t$ for horizon $T = 5000$, for problem $2$.}
    \label{fig:6:meanRegretPb2}
\end{figure}

@@

% -----------------------------------------------------------------
\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.00\linewidth]{2-Chapters/6-Chapter/nonstatbandits.git/figures/SP__K3_T5000_N1000__9_algos_pb1/main_HistogramsRegret_shareX____env1-1_1316297932259102962.pdf}
    \caption{Histograms of the distributions of regret $R_T$ ($T=5000$) for problem 1.}
    \label{fig:6:histogramRegretPb1}
\end{figure}

>>>>

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.09\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/6_Problems/Problem_1.pdf}
    \caption{Problem $1$: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on only one arm at a time (\ie, $C=4$).
        The means are in $[0,1]$, and there are $C+1=5$ stationary intervals of equal lengths.
        Some changes do not modify the optimal arm (\eg, at $T=1000$ and $T=4000$) and others do.
    }
    \label{fig:6:Problem_1}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.09\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/6_Problems/Problem_2.pdf}
    \caption{Problem $2$: $K=3$ arms with $T=5000$, and $\Upsilon=4$ changes occur on all arms (\ie, $C=12$).
        The means are again in $[0,1]$, and there are also $C+1=5$ stationary intervals of equal lengths.
        % Some changes do not modify the optimal arm, but the mean of each arm does change at all change-points.
    }
    \label{fig:6:Problem_2}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/6_Problems/Problem_5.pdf}
    \caption{Problem $3$: $K=6$, $T=20000$, $C=19$ changes occur on most arms at $\Upsilon=8$ break-points.}
    \label{fig:6:Problem_5}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/6_Problems/Problem_4.pdf}
    \caption{Problem $4$: $K=3$, $T=5000$, $C=12$ changes occur on all arms at $\Upsilon=4$ break-points.}
    % \caption{\textbf{Problem 4}: $K=3$ arms with $T=5000$, $\Upsilon=4$ changes occur on all arms at a time (\ie, $C=12$).}
    \label{fig:6:Problem_4}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.05\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/6_Problems/Problem_6.pdf}
    \caption{Pb $5$: $K=5$, $T=100000$, $C=179$ changes occur on some arms at $\Upsilon=81$ break-points.}
    % \caption{\textbf{Problem 5}: $K=5$, $T=100000$, $\Upsilon=81$ changes occurring on some arms at every time ($C=179$).}
    \label{fig:6:Problem_6}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.15\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/SP__K3_T5000_N1000__9_algos_pb1/main____env1-1_1316297932259102962.pdf}
    \caption{Mean regret as a function of time, $R_t$ for horizon $T = 5000$, for problem 1.}
    \label{fig:6:meanRegretPb1}
\end{figure}

% -----------------------------------------------------------------
\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.09\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/SP__K3_T5000_N1000__9_algos_pb2/main____env1-1_7882655236216606305.pdf}
    \caption{Mean regret as a function of time, $R_t$ for horizon $T = 5000$, for problem $2$.}
    \label{fig:6:meanRegretPb2}
\end{figure}

@@

% -----------------------------------------------------------------
\begin{figure}[h!]  % [htbp]
    \centering
    \includegraphics[width=1.00\linewidth]{2-Chapters/6-Chapter/nonstatbandits/figures/SP__K3_T5000_N1000__9_algos_pb1/main_HistogramsRegret_shareX____env1-1_1316297932259102962.pdf}
    \caption{Histograms of the distributions of regret $R_T$ ($T=5000$) for problem 1.}
    \label{fig:6:histogramRegretPb1}
\end{figure}
